\documentclass[a5paper,onecolumn,final,10pt]{memoir}

% -------- %
% Preamble %
% -------- %

\usepackage[stretch=10]{microtype}
\usepackage[utf8]{inputenc}
\usepackage[british]{babel}
\usepackage{csquotes}

\usepackage[whole]{bxcjkjatype}

\usepackage{times}
\usepackage{courier}
\usepackage[T1]{fontenc}
\input{unicode}

\usepackage[svgnames]{xcolor}
\usepackage{graphicx}

\usepackage{amsmath}
%\usepackage{amssymb}
%\usepackage{amsfonts}
%\allowdisplaybreaks[3]
%\usepackage{amsthm}
%\usepackage{mathtools}
\usepackage{siunitx}

\usepackage{enumitem}

\newcommand{\eqv}{\mathrel{\mkern3mu\Leftrightarrow\mkern3mu}}
\newcommand{\imp}{\mathrel{\mkern3mu\Rightarrow\mkern3mu}}

\usepackage{tikz}
\usetikzlibrary{shapes,arrows,positioning,calc,decorations,arrows.meta}
\input{tikz}

\definecolor{linkblue}{HTML}{0066cc}
\usepackage[
	hidelinks,  % Tirar as cores dos links
	unicode,
	colorlinks=false,
	linkcolor=MidnightBlue,
	citecolor=Green,
	urlcolor=linkblue,
]{hyperref}

\usepackage[backgroundcolor=yellow!50,textsize=tiny]{todonotes}



% ----- %
% Style %
% ----- %

% Margins
\setlrmarginsandblock{1.5cm}{*}{*}
\setulmarginsandblock{3cm}{*}{1.2}
\checkandfixthelayout

% Chapter headers
\chapterstyle{plain}
%\cftsetindents{chapter}{1.5em}{2.3em}
%\renewcommand\cftchapterfont{\normalfont}
%\renewcommand\cftchapterleader{\cftdotfill{\cftsectiondotsep}}
%\renewcommand\cftchapterpagefont{\normalfont}
%\renewcommand\cftchapterafterpnum{\par\vskip-10pt}
\counterwithout{section}{chapter}

% Section headers
\setsubsubsecheadstyle{\sffamily\itshape}
\setsecheadstyle{\sffamily\bfseries}
\setsubsecheadstyle{\sffamily\bfseries}

% Line spacing
\OnehalfSpacing

% Header/footer
\createmark{section}{right}{nonumber}{}{}
\makeevenhead{headings}{\thepage}{}{\sffamily\MakeUppercase{Quick-start guide}}
\makeoddhead {headings}{\sffamily\rightmark}{}{\thepage}
%\makeheadrule{headings}{\textwidth}{0.4}

\makeatletter
\let\@copyright@old\copyright
\def\copyright{\makebox[.6ex][l]{\hspace{-.4ex}\textsuperscript{\@copyright@old}}}
\makeatother

% -------- %
% Document %
% -------- %

\newcommand\machinename%
%	{SNX-800B Type 5}
%	{STR-800B \textsf{\textit{Super}}}
	{\textsf{TAU-800B \textit{Super}}}

\newcommand\companyname%
%	{Aperture Science\,\copyright}
	{Jikan Systems Corp.\copyright}
	
% Shortcut since we use monospace so much
\let\ttt\texttt
%\newcommand\t[1]{\texttt{#1}}




\begin{document}

\frontmatter

\begin{titlingpage}
	\calccentering{\unitlength}
	\begin{adjustwidth*}{\unitlength}{-\unitlength}
		\centering

		\vspace*{4\baselineskip}

		\begin{tikzpicture}
			\node[rectangle,draw,very thick,inner sep=18pt,align=center] {
			{\HUGE \machinename}
			\\[32pt]
			{\LARGE Quick-start guide}
			};
		\end{tikzpicture}

		\vfill

		{\footnotesize \companyname \\ 時間システム Corp.\copyright}
	\end{adjustwidth*}
\end{titlingpage}



\thispagestyle{empty}

\begin{footnotesize}
	\noindent
  This is a quick-start guide to your Time Arithmetic Unit (revision 800-B, \textit{Super} edition) time-assisted computing machine.
	Please ensure you have thoroughly read and understood the User Manual and the Warranty Disclaimer before attempting to utilize the machine.
	\companyname{} is not responsible for any damages resulting from improper use of the time jump facilities of this machine.
	\vfill
	\warningbox{%
		\textbf{\textsf{Please ensure that the Novikov module has sufficient power throughout the operation of the machine. Failure to supply the minimum rated power may cause time inconsistency paradoxes.}} \\[2pt]
		In the unlikely case of forced inconsistency contact our hotline \\
		\hfill\textsf{\textbf{1-800-NOTIME}}}
\end{footnotesize}



\clearpage
\renewcommand\cftchapterfont{\ttfamily}
\renewcommand\cftchapterleader{\ttfamily\cftdotfill{.}}  % Bué intuitivo, escuta
\renewcommand\cftchapterpagefont{\ttfamily}
%\show\tableofcontents
\tableofcontents*



\mainmatter

\section{Introduction}
\vspace*{-20pt}\rule{\textwidth}{0.8pt}

\noindent
Congratulations of becoming the proud owner of a \machinename{}, the latest technology in time-based computing. The following document serves as an introduction to the architecture and operation modes of this time-assisted arithmetic computing unit, as well as to any other extensions offered by \companyname{} compatible with the \machinename{} that were acquired as part of your commercial agreement.

For more information regarding available computing extension hardware compatible with your computing unit contact your local \companyname{} sales representative. Missing documentation of acquired computing extension hardware and advanced time operation modes of the computing unit can be obtained upon written request with proof of purchase to \companyname{} Main Shenzen Headquarters.
\todo{Jikan=japão, mas Shenzen=china?}

Please note that this document \underline{does not} preclude the consultation of the complete reference manual, which should have been provided to you alongside this document and the computing unit. If the complete reference manual was not provided to you upon purchase, please contact your local sales representative.

\companyname{} is not liable for damages incurred in the misuse of the equipment to the extent of but not limited to the operation modes described in this document.

\clearpage
\section{The Machine Language}
\vspace*{-20pt}\rule{\textwidth}{0.8pt}

\noindent
The following is a quick-reference guide to \machinename{} assembly language. Please use ONLY the officially licensed assembler programs by \companyname{} (ensure you have been supplied with all 9 (nine) floppy diskettes for installation of the assembler).

%The CPU word size is 8 bits.

Quick facts:
\begin{itemize}[nosep]
	\item 6-bit word size, 12-bit address space with pageable memory.
	\item 0.66\,MHz clock speed.
	\item Four general purpose word registers.
	\item Six-word stack.
	\item Time jumps of up to 200 clock cycles in any direction.\footnotemark
	\item Memory-mapped IO.
	\item Big endian.
\end{itemize}
%
\footnotetext{
	Note: for jumps of over 80 clock cycles an upgraded SPS-3-6000 power supply with at least 6\,kW of peak power output must be purchased. \textbf{Serious damage may occur if you attempt to use these operations without sufficient power!}}

\subsection*{CPU registers}

The CPU has a total of 10 (ten) words of register memory. 
Of these, 5 (five) words are general-purpose registers 
and 5 (five) are special-purpose registers. 

The general purpose registers are the following: \ttt{A}, \ttt{BH}, \ttt{BL}, \ttt{CH}, \ttt{CL}. 
The latter two pairs of registers can be used to store 2-word values, high word and low word respectively. 
These registers are used readable and writable via move and arithmetic-logic instructions. 

%Then, the CPU has one flag register \ttt{F}, where each bit has the following meaning (left to right: \ttt{SZ--NC})
%\begin{itemize}
%\item[A]
%\end{itemize}
Then, the CPU has one flag register \ttt{F}, 
%with the following bits: \verb|N--PZC|, respectively negative, parity, zero, and carry flags. 
%with the following bits: \verb|N---ZC|, respectively negative, zero, and carry flags. 
with the following bits: \verb|NV--ZC|, respectively negative, overflow, zero, and carry flags. 
These are set and cleared by arithmetic and logical instructions, 
and can be queried by the conditional branch instructions. 
The flag register cannot be written to, but it can be read and copied to memory or another register. 
\todo{Se calhar é melhor não se copiar e pronto}

The \ttt{X} register is an index register: it can be read and written to like a general purpose register, 
%and it can be added as an offset to a location in memory 
and it can be used in the indexed addressing mode to access a location obtained by adding the contents of the register to a base address. 

The CPU also has a stack pointer, that points to one-past the top of the stack. 
It can be read or written to as a general purpose register, but it is also altered by the \ttt{CAL}, \ttt{RET}, \ttt{PSH}, \ttt{POP} instructions. 

Finally, the two-word program counter stores the address of the next instruction, and can be modified by jump, branching and subroutine instructions

12-bit addresses are read and stored as two words in big-endian order: \ttt{\%llhh}.
In order to perform 12-bit arithmetic, you must process the two words manually.\footnotemark

\footnotetext{Advanced mathematical subroutines are available for purchase, please contact your regional sales representative.}

\subsection*{Addressing modes}

The following addressing modes are available:

%\begin{itemize}[nosep]
%	\item Register \ttt{\%a}: addresses a named register.
%	\item Immediate \ttt{\#ff}: represents a literal one-word value.
%	\item Immediate \ttt{\#fff}: represents a literal two-word value.
%	\item Absolute \ttt{\%llhh}: the memory address $\ttt{ll}+2^8\ttt{hh}$.
%	\item Indexed \ttt{\%llhh,X}: the memory address $\ttt{ll}+2^8\ttt{hh}+\textrm{contents of \ttt{X}}$.
%	\item Indirect \ttt{(\%llhh)}: the address stored at memory address $\ttt{ll}+2^8\ttt{hh}$.
%	\item Indirect \ttt{(\%b)} \ttt{(\%c)}: the address $\ttt{c}$
%\end{itemize}

% Estas tabelas com linhas em todo o lado são péssimas xD mas faz parte da aesthetic, que achas?
\begin{center}
\begin{tabular}{|l|l|l|}
	\hline
	\textbf{Mode} & \textbf{Notation} & \textbf{Description} \\ \hline
	Register  & \ttt{\%a} & a named register \\ \hline
	Immediate & \ttt{\#ff} & represents a literal one-word value \\ \hline
	Immediate & \ttt{\#fff} & represents a literal two-word value \\ \hline
	Absolute  & \ttt{\%llhh} & the memory address $\ttt{ll}+2^6×\ttt{hh}$ \\ \hline
	Indexed   & \ttt{\%llhh,X} & the memory address $\ttt{ll}+2^6×\ttt{hh}+\textrm{contents of \ttt{X}}$ \\ \hline
	Indirect  & \hspace{-0.2em}\ttt{(\%llhh)} & the address stored at memory address $\ttt{ll}+2^6×\ttt{hh}$  \\ \hline
%	Indirect  & \hspace{-0.2em}\ttt{(\%b)}\,\ttt{(\%c)} & the address stored at memory address $\ttt{bh}$ (resp c)\\ \hline
	Indirect  & \hspace{-0.2em}\ttt{(\%r)}\footnotemark & the address stored at memory address $\ttt{rl}+2^6×\ttt{rh}$ \\ \hline
\end{tabular}
\end{center}

\footnotetext{Where \ttt{r} is \ttt{b} or \ttt{c}.}

\subsection*{List of instructions}

The following is a quick-reference list of instructions. 

\newcommand\instruction[2]{%
	\noindent
	\begin{minipage}[t]{0.22\textwidth} \texttt{#1} \end{minipage}
	\hspace{0.03\textwidth}
	\begin{minipage}[t]{0.75\textwidth} #2 \end{minipage}
%	\medskip
	\vspace*{-0.5\smallskipamount}
}

\noindent
\textit{\small Note: unless otherwise noted, instructions that 「set the \ttt{Z} flag」 set it if the result is zero, and clear it otherwise, instructions that 「set the \ttt{N} flag」 set it to the value of the most significant bit of the result (i.e.\ set if negative, clear otherwise); and instructions that  set the \ttt{V} flag」  set it to the value of the second most significant bit of the result (i.e.\ set if signed arithmetic overflows, clear otherwise).}. 
\subsubsection*{Memory}

\instruction{MOV src dst}{Set word at \texttt{dst} to contents of \texttt{src}. \\ Flags: set \ttt{Z}, \ttt{N}, \ttt{V}.}

\instruction{PSH src}{Push \ttt{src} onto the stack and increment \ttt{sp}.}

\instruction{POP dst}{Pop value on the top of the stack onto \ttt{dst} and decrement \ttt{sp}.}

\subsubsection*{Arithmetic}

\instruction{ADD src dst}{%
	Set word at \texttt{dst} to $\texttt{src}+\texttt{dst}+\ttt{C}$. \\ 
	Flags: set \ttt{Z}, \ttt{N}, \ttt{V}, set \ttt{C} on overflow. 
}

\instruction{SUB src dst}{%
	Set word at \texttt{dst} to $\texttt{src}-\texttt{dst}-\overline{\ttt{C}}$. \\ 
	Flags: set \ttt{Z}, \ttt{N}, \ttt{V}, set \ttt{C} on underflow. 
}

\instruction{MUL src dst}{%
	Set word at \texttt{dst} to $\texttt{src}×\texttt{dst}$, where operands are unsigned values. \\ 
	Flags: set \ttt{Z}, \ttt{N}, \ttt{V}, set \ttt{C} on overflow.
}

\instruction{MUS src dst}{%
	Set word at \texttt{dst} to $\texttt{src}×\texttt{dst}$, where operands are signed values. \\ 
	Flags: set \ttt{Z}, \ttt{N}, \ttt{V}, set \ttt{C} on overflow.
}

%\todo{Como fazer handle de divisoes por zero?}
\instruction{DIV src dst}{%
	Set word at \texttt{dst} to $\texttt{src}\div\texttt{dst}$, where operands are unsigned values. \\
	Flags: set \ttt{Z}. 
}

\instruction{DIS src dst}{%
	Set word at \texttt{dst} to $\texttt{src}\div\texttt{dst}$, where operands are signed values. \\
	Flags: set \ttt{Z}. 
}

\renewcommand\mod%
	{\mathrel{\mathrm{mod}}}

\instruction{MOD src dst}{%
	Set word at \texttt{dst} to $\texttt{src}\mod\texttt{dst}$, where operands are unsigned values. \\
	Flags: set \ttt{Z}. 
}

\instruction{MOS src dst}{%
	Set word at \texttt{dst} to $\texttt{src}\mod\texttt{dst}$, where operands are signed values.\\
	Flags: set \ttt{Z}.  
}


\instruction{AND src dst}{%
	Set word at \ttt{dst} to bitwise-and of \ttt{src} and \ttt{dst}. \\
	Flags: set \ttt{Z}, \ttt{N}, \ttt{V}. 
}

\instruction{OR~ src dst}{%
	Set word at \ttt{dst} to bitwise-or of \ttt{src} and \ttt{dst}. \\
	Flags: set \ttt{Z}, \ttt{N}, \ttt{V}. 
}

\instruction{XOR src dst}{%
	Set word at \ttt{dst} to bitwise-xor of \ttt{src} and \ttt{dst}. \\
	Flags: set \ttt{Z}, \ttt{N}, \ttt{V}. 
}

\instruction{NOT dst}{%
	Set word at \ttt{dst} to bitwise-not of \ttt{dst}. \\
	Flags: set \ttt{Z}, \ttt{N}, \ttt{V}. 
}

\instruction{LSL dst}{%
	Shift bits in \ttt{dst} to the left. \\ 
	Flags: set \ttt{Z}, \ttt{N}, \ttt{V}, set \ttt{C} on overflow.  
}

\instruction{LSR dst}{%
	Shift bits in \ttt{dst} to the right. \\ 
	Flags: set \ttt{Z}, \ttt{N}, \ttt{V}. 
}



\subsubsection*{Comparison}

\instruction{CMP src dst}{Flags: set \ttt{C} to $\texttt{src}>\texttt{dst}$, set \ttt{Z} to $\texttt{src}=\texttt{dst}$.}

\instruction{BIT src dst}{Flags: set \ttt{Z} to $\neg(\texttt{src}\land\texttt{dst})$.}
%Set \ttt{N} to msb of $\ttt{src}\land\ttt{dst}$.




\subsubsection*{Jump}

\instruction{JMP addr}{Jump execution to \texttt{addr} (two-word address).}

\subsubsection*{Branching}

\instruction{BCC off}{Branch to $\ttt{pc}+\ttt{off}$ if \ttt{C} clear (signed offset).}

\instruction{BCS off}{Branch to $\ttt{pc}+\ttt{off}$ if \ttt{C} set (signed offset).}

\instruction{BNE off}{Branch to $\ttt{pc}+\ttt{off}$ if \ttt{Z} clear (signed offset).}

\instruction{BEQ off}{Branch to $\ttt{pc}+\ttt{off}$ if \ttt{Z} set (signed offset).}

\instruction{BPL off}{Branch to $\ttt{pc}+\ttt{off}$ if \ttt{N} clear (signed offset).}

\instruction{BMI off}{Branch to $\ttt{pc}+\ttt{off}$ if \ttt{N} set (signed offset).}

\subsubsection*{Control}

\instruction{CLC}{Clear carry flag}

\instruction{SEC}{Set carry flag}

\subsubsection*{Subroutines}

\instruction{CAL dst}{Store current \texttt{pc} in stack, increment \texttt{sp}, and jump to \texttt{dst}.}

\instruction{RET~~~~}{Read \texttt{pc} from stack, decrement \texttt{sp}, and jump.}

\subsubsection*{Miscellaneous}

\instruction{NOP}{No-op.}



\end{document}
